New_Data_Coherence

### 2019-10-13 Analysis/04_Coherence_Calculations.Rmd
More fixes

#String
string_p = readRDS("./data/Permutation_Results/string_p_1k.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)

>>>>

#String
string_p = readRDS("./data/Permutation_Results/Complete_10k_String.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)
string_p <- string_p[!duplicated(string_p[, 1]), ] # Fix "Attention deficit hyperactivity disorder" that was run twice
